---
title: "binomial-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```


## Binomial Distributions

This package allows to create various forms of Binomial Distributions such that the user can access methods that allow them to calcluate certain probabilities, given the number of trials and successes.

## bin_choose

The following function allows the user to engage in combanitorics and find n choose k.

```{r}
bin_choose(4, 3)
```

In the example above, 4 choose 3 is the same as 4! / 3! = 4.

## bin_probability 

The following function allows the user to engage in combanitorics and find probability given success, number of trials, and probability of success.

```{r}
bin_probability(3, 5, 0.5)
```

It can be seen that this is the same as (5 choose 3) * (0.5 ^ 3) * (0.5 ^ 2) = 0.3125

## bin_distribution

The following function allows the user to engage in combanitorics and find several probabilities for a range of different success values that are less than the number of trials. It's plot is a histogram, with successes on x and probability on y. An example can be found in the code chunk below:

```{r}
bin1 <- bin_distribution(5, 0.5)
bin1
plot(bin1)
```
## bin_cumulative

The following function allows the user to engage in combanitorics and find several probabilities for a range of different success values that are less than the number of trials. It's plot is a line, with successes on x and probability on y. Furthermore, it adds all previous probabilities to display that the sum of all probabilities = 1. An example can be found in the code chunk below:

```{r}
bin1 <- bin_cumulative(5, 0.5)
plot(bin1)
```

## bin_mean

The following function allows the user to find the mean of a given binomial distribution = np.

```{r}
bin_mean(5, 0.5)
```

## bin_variance
The following function allows the user to find the variance of a given binomial distribution = np(1 - p).

```{r}
bin_variance(5, 0.5)
```

## bin_mode
The following function allows the user to find the mode of a given binomial distribution = int(np + p).
```{r}
bin_mode(5, 0.5)
```

## bin_skewness
The following function allows the user to find the skewness of a given binomial distribution = (1 - 2p) / sqrt(variance).
```{r}
bin_skewness(10, 0.3)
```
## bin_kurtosis
The following function allows the user to find the kurtosis of a given binomial distribution = (1 - 6p(1 - p)) / variance.
```{r}
bin_kurtosis(10, 0.3)
```
